### 2023-02-01 paper-reviews/papers-2023.tex
Add Centaur AI accelerator paper

    \cite{Wheeler:Optical-AI:2019}.
\end{itemize}

>>>>

    \cite{Wheeler:Optical-AI:2019}.

    \item Centaur has developed an x86 processor with deep-learning accelerator --- Ncore. The accelerator has a typical design for the field of application: it's a VLIW architecture relying on traditional SIMD approach with smaller sized vector elements like INT8, BF16, etc. The architecture is 64 times wider that Intel's AVX-512. The x86 cores are alike low-end Skylake cores but it can achieve better neural network performance thanks to the accelerator. Centaur has also constructed a basic software stack that convert TensorFlow to an internal graph format that is later compiled into Ncore assembly - another typical approach for deep-learning accelerators. The article reports that so fat Centaur's software can only handle inference but not training.

    \cite{Gwennap:Centaur-AI:2019}.
\end{itemize}
